### 2020-10-13 manuscript/manuscript.rmd
successfully reknit when move the read functions back to the manuscript

---
bibliography: manuscript.bib
csl: nature.csl
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document: default
  github_document: default
---

@@

  result_colors = c( cbPalette[2], cbPalette[4], cbPalette[1] )
  names( result_colors ) = c( "Ctenophora-sister", "Porifera-sister", "Unresolved" )

@@

@@

**Extended Data Table 1.** Table 1. Overview of data matrices used in this study.
```{r table_study_summary}

opts <- options(knitr.kable.NA = "")
knitr::kable(table_study_summary) %>%
  kable_styling(full_width = F)

@@

>>>>

---
bibliography: manuscript.bib
csl: nature.csl
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
  word_document: default
  github_document: default
---

@@

  result_colors = c( cbPalette[2], cbPalette[4], cbPalette[1] )
  names( result_colors ) = c( "Ctenophora-sister", "Porifera-sister", "Unresolved" )
  cat_categories = read_tsv("../data_processed/tables/cat_categories.tsv")
table_study_summary = read_tsv("../data_processed/tables/study_summary.tsv")
taxa_map_whelan=read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv") %>% filter(original_matrix=="../considered_data/Whelan2017/strict.phy")
taxa_map_philippe=read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv") %>% filter(original_matrix=="../considered_data/Philippe2009/Philippe2009.nex")
tree1= read.tree("../trees_new/iqtree/Whelan2017_strict.model_test.treefile")
tree2=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT60.con.tre")
tree3=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT90.con.tre")
tree4=read.tree("../trees_new/phylobayes/Whelan2017_strict.bpcomp.con.tre")
tree5=read.tree("../trees_new/phylobayes/Whelan2017_strict.phy_GTR_CAT.con.tre")
tree6= read.tree("../trees_new/iqtree/Philippe2009_only_choanozoa.WAG+C60.treefile")
tree7=read.tree("../trees_new/sensitive/Philippe2009_only_choanozoa.phy_Poisson_CAT60.con.tre")
tree8=read.tree("../trees_new/sensitive/Philippe2009_only_choanozoa.phy_Poisson_CAT150.con.tre")
tree9=read.tree("../trees_new/phylobayes/Philippe2009_only_choanozoa.bpcomp.con.tre")
tree10=read.tree("../trees_new/phylobayes/Philippe2009_only_choanozoa.phy_GTR_CAT.con.tre")
ribo = read_tsv("../data_processed/tables/ribosomal_gene.tsv")
busco = read_tsv("../data_processed/tables/busco_gene.tsv")
cross_validation =
  read_tsv("../data_processed/tables/cross_validation.tsv") %>%
  gather("model", "score", `nCAT60`, `Poisson-CAT`)

@@

# https://www.datanovia.com/en/lessons/t-test-in-r/
cross_validation %>%
  group_by(matrix,model)
# Whelan
Dw = cross_validation %>%
  filter(matrix=="Whelan2017_strict")

stat_test_w =
  t.test(score ~ model, var.equal = TRUE, data=Dw)
P_value_Whelan2017_strict=stat_test_w$p.value

# Philippe
Dp = cross_validation %>%
  filter(matrix=="Philippe2009_Chanimalia")

stat_test_p =
    t.test(score ~ model, var.equal = TRUE, data=Dp)

P_value_Philippe2009=stat_test_p$p.value
```

@@

**Extended Data Table 1.** Table 1. Overview of data matrices used in this study.
```{r table_study_summary}
table_study_summary = read_tsv("../data_processed/tables/study_summary.tsv")
opts <- options(knitr.kable.NA = "")
knitr::kable(table_study_summary)

@@

cross_validation =
  read_tsv("../data_processed/tables/cross_validation.tsv") %>%
  gather("model", "score", `nCAT60`, `Poisson-CAT`)

```{r cross_validation, fig.width=6, fig.height=3.5}
p_w = cross_validation %>%
  filter(matrix=="Whelan2017_strict") %>%
  ggplot(aes(x=model, y=score)) +
  geom_boxplot() +
  ggtitle("Whelan2017") +
  theme_classic()
p_p = cross_validation %>%
  filter(matrix=="Philippe2009_Chanimalia") %>%
  ggplot(aes(x=model, y=score)) +
  geom_boxplot() +
  ggtitle("Philippe2009") +
  theme_classic()
ggarrange(
  p_w,
  p_p,
  ncol=2, labels = c("A", "B"))

**Extended Data Fig. 10.** Cross validation..
